**fabryka**

### 2025-07-14 README.Rmd
correction of fabryka shiny application and description article after first round of review in PCI archaeology
correction of fabryka article and shiny application after first round of review in PCI archaeology

```{=html}
<style>
body {
text-align: justify}
</style>
```

@@

* clone the fabryka repository from GitHub: <https://github.com/marchaeologist/fabryka> or download the code in "Code" and "Download ZIP" at the same address. This will give you the latest version of the source code. The application can be launched by opening the app.R file in the main folder and by running the following commands:

```{r, eval=FALSE}

pkgload::load_all(".")
fabryka()

>>>>

@@

* clone the fabryka repository from GitHub: <https://github.com/marchaeologist/fabryka> or download the code in "Code" and "Download ZIP" at the same address. This will give you the latest version of the source code.

* Open fabryka.Rproj

* If you are using the application for the first time, you have to install several packages used in the application. Lists of all these packages and dependencies are available in a DESCRIPTION file and a DEPENDECIES file in the github repository. To install fabryka packages and dependencies, copy and paste the following code lines into the R console:

```{r packages_dep, eval=FALSE}

fabryka_packages = c("shiny", "dplyr","ggplot2","plotly", "ggsci", "ggtern", "circular", "CircStats", "Ternary", 
                   "RStoolbox", "shinyjs", "rmarkdown", "shinythemes",  "ggalt", "DT", "raster")

is_installed = sapply(fabryka_packages, require, character.only=T)

sapply(fabryka_packages[!is_installed], install.packages)

The application can be launched by opening the app.R file in the main folder and pressing "Run App" or by running the following commands:

```{r run_app, eval=FALSE}

pkgload::load_all(".")

fabryka()

### 2025-07-14 fabryka_pci/article.Rmd
correction of fabryka article and shiny application after first round of review in PCI archaeology

# Useful links

-   use fabryka online: <https://marchaeologist.shinyapps.io/fabryka/>
    \smallbreak
-   If you are preparing a mission in a field without Internet access:

Install [R](https://www.r-project.org) and [Rstudio
Desktop](https://posit.co/download/rstudio-desktop/).

Clone the fabryka repository from GitHub:
<https://github.com/marchaeologist/fabryka> or download the code in
"Code" and "Download ZIP" at the same address. This will give you the
latest version of the source code. The application can be launched by
opening the app.R file in the main folder and by running the following
commands:

@@

pkgload::load_all(".")
fabryka()

@@

If you are using the application for the first time, Rstudio will install several packages used in the application. Lists of all these packages and dependencies are available in a DESCRIPTION file and a DEPENDECIES file in the github repository.

-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka:
    <https://doi.org/10.5281/zenodo.15207419> \smallbreak
-   Zenodo repository of this article:
    <https://doi.org/10.5281/zenodo.15879462> \bigbreak

>>>>

# Useful links and tips

-   use fabryka online: <https://marchaeologist.shinyapps.io/fabryka/> \smallbreak
-   source code: <https://github.com/marchaeologist/fabryka/tree/main> \smallbreak
-   Report bugs or any request: <https://github.com/marchaeologist/fabryka/issues> \smallbreak
-   github reprository doi of fabryka: <https://doi.org/10.5281/zenodo.15207419> \smallbreak
-   Zenodo repository of this article: <https://doi.org/10.5281/zenodo.15879462> \bigbreak

**If you are preparing a mission in a field without Internet access:**

1. Install [R](https://www.r-project.org) and [Rstudio
Desktop](https://posit.co/download/rstudio-desktop/).

2. Clone the fabryka repository from GitHub:
<https://github.com/marchaeologist/fabryka> or download the code in
"Code" and "Download ZIP" at the same address. This will give you the
latest version of the source code.

3. Open fabryka.Rproj

4. If you are using the application for the first time, you have to install several packages used in the application. Lists of all these packages and dependencies are available in a DESCRIPTION file and a DEPENDECIES file in the github repository. To install fabryka packages and dependencies, copy and paste the following code lines into the R console:

```{r packages_dep, eval=FALSE}

fabryka_packages = c("shiny", "dplyr","ggplot2","plotly", "ggsci", "ggtern", "circular", 
                     "CircStats", "Ternary", "RStoolbox", "shinyjs", "rmarkdown", 
                     "shinythemes",  "ggalt", "DT", "raster")

is_installed = sapply(fabryka_packages, require, character.only=T)

sapply(fabryka_packages[!is_installed], install.packages)

5. The application can be launched by opening the app.R file in the main folder and pressing "Run App" or by running the following commands:

@@

pkgload::load_all(".")

fabryka()

@@
